Supplementary Information

### 2021-02-04 writing/transect_supplement.Rmd
side-by-side zoomed scales for accumulation curves instead of log-log plots

(ref:read-compare-asv) Comparison between ASV read abundances for different sequencing strategies

(ref:read-compare) which were detected by one sequencing strategy but not the other are plotted as tick marks along the axes. Dashed line represents a constant ratio of read numbers. The blue line is a LOESS smooth of the data, with associated uncertainty in grey shading. $R^2$ value displayed is for log-transformed non-zero read numbers.

```{r read-compare-asv, fig.cap="(ref:read-compare-asv). ASVs (ref:read-compare)", fig.scap="(ref:read-compare-asv)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
grid::grid.newpage()
grid::grid.draw(
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "ASV"
  )
)
```

(ref:read-compare-otu) Comparison between OTU read abundances for different sequencing strategies

```{r read-compare-otu, fig.cap="(ref:read-compare-otu). OTUs (ref:read-compare)", fig.scap="(ref:read-compare-otu)", cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
grid::grid.newpage()
grid::grid.draw(
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "OTU"
  )
)
```

(ref:accum-OTU-s) OTU accumulation curves

(ref:accum-OTU) Each curve represents rarefaction of a single sample or pooled pair of samples. Points at the end of each curve represent the actual read depth and observed OTU richness. Note logarithmic axes.

>>>>

(ref:read-compare-s) Comparison between read numbers for different sequencing strategies

(ref:read-compare) by ASV (**a**) and 97% OTU (**b**). ASVs/OTUs which were detected by one sequencing strategy but not the other are plotted as tick marks along the axes. Dashed line represents a constant ratio of read numbers. The blue line is a LOESS smooth of the data, with associated uncertainty in grey shading. $R^2$ value displayed is for log-transformed non-zero read numbers.

```{r read-compare, fig.cap="(ref:read-compare-s), (ref:read-compare)", fig.scap="(ref:read-compare-s)", fig.height=8, cache=TRUE, extra.cache=gethash("multi_table","comparisons")}
ggpubr::ggarrange(
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "ASV"
  ),
  read_comparison(
    readd(multi_table),
    readd(comparisons),
    type = "OTU"
  ),
  ncol = 1,
  labels = "auto",
  label.x = 0.9
)
```

(ref:accum-OTU-s) 97% OTU accumulation curves

(ref:accum-OTU) Each curve represents rarefaction of a single sample or pooled pair of samples. Points at the end of each curve represent the actual read depth and observed OTU richness. Panel at left has enlarged scale to show PacBio more clearly.
